    \documentclass[10pt,a4paper,sans]{moderncv}
    \moderncvstyle{banking}
    \moderncvcolor{black}
    \nopagenumbers{}

    \usepackage[utf8]{inputenc}
    \usepackage[top=0.2cm, bottom=0.2cm, left=0.3cm, right=0.3cm]{geometry} % ultra-compact margins
    \usepackage{ragged2e}
    \usepackage{multicol}
    \usepackage{enumitem}
    \usepackage{amssymb}
    \usepackage{fontawesome5}
    \usepackage{xcolor}
    \usepackage{hyperref}
    \hypersetup{colorlinks=true, urlcolor=blue}


    % Custom cventry
    \newcommand*{\customcventry}[7][.10em]{%
    \begin{tabular}{@{}l}
        {\bfseries #4} \\
        {\itshape #3}
    \end{tabular}
    \hfill
    \begin{tabular}{l@{}}
        {\bfseries #5} \\
        {\itshape #2}
    \end{tabular}
    \ifx&#7&%
    \else{\\
    \begin{minipage}{\maincolumnwidth}%
        \footnotesize#7%
    \end{minipage}}\fi%
    \par\addvspace{#1}
    }

    \begin{document}

    % Ultra-compact header block
    \begin{center}
        {\fontsize{18}{20}\selectfont\textbf{Ahmed MAKROUM}} \\
        \vspace{0.05em}
        \footnotesize Data Engineer and Full-Stack Web/Mobile Developer \\
        \vspace{0.05em}
        {\normalsize
            \faMobile\enspace +212 664715219 \quad
            \faEnvelope\enspace ahmedmakroum3@gmail.com \quad
            \faHome\enspace Casablanca, Morocco \\
            \faLinkedin\enspace \href{https://www.linkedin.com/in/ahmed-makroum/}{in/ahmedmakroum} \quad
            \faGithub\enspace \href{https://github.com/ahmedmakroum}{github.com/ahmedmakroum} \quad
            \faGlobe\enspace \href{https://ahmedmakroum.github.io/AhmedMakroumPortfolio/}{makroum.me}
        }
    \end{center}
\vspace{-18pt}

    % PROFILE
\section{Profile}
\vspace{-6pt}
\justifying
Results-driven Computer and Network Engineer (MIAGE: Applied Methods for Business Management) with a strong foundation in software engineering, data engineering, and full-stack development. Adept at building robust data pipelines, developing scalable web/mobile applications, and leveraging cloud and open-source technologies. Recognized for adaptability, teamwork, and a passion for continuous learning.


    % EXPERIENCE
    \vspace{-15pt}
    \section{Experience}

    \customcventry{03/2025 ‐ Present}{\href{https://www.allianz.ma}{Allianz Maroc}}{Data Engineer}{}{}{
    \begin{itemize}[leftmargin=0.5cm, itemsep=0pt, topsep=0pt]
    \item Designed and deployed end-to-end data pipelines using NiFi and Spark to extract, clean, and load data from internal insurance systems.
    \item Consolidated fragmented sources into a PostgreSQL warehouse, enabling unified and consistent reporting.
    \item Delivered real-time dashboards with Metabase, improving data accessibility for business users.
    \item Currently developing and maintaining a web application to manage and track healthcare payments issued by Allianz to external providers, using Spring Boot and Next.js.
    \end{itemize}}

    \customcventry{06/2024 ‐ 08/2024}{\href{https://boti.education/}{BOTI School}}{Data Engineer}{}{}{
    \begin{itemize}[leftmargin=0.8cm, itemsep=0pt, topsep=0pt]
    \item Developed a scalable ETL pipeline using Apache Beam on Google Cloud to process learning activity logs.
    \item Transformed raw data into structured datasets, enabling clear insights into user behavior and engagement.
    \item Delivered automated reporting through Looker dashboards for the executive team.
    \end{itemize}}

    \customcventry{06/2023 ‐ 08/2023}{\href{https://6solutions.com/}{6solutions}}{Web and Mobile Developer}{}{}{
    \begin{itemize}[leftmargin=0.8cm, itemsep=0pt, topsep=0pt]
    \item Developed a cross-platform consulting platform for legal, medical, and financial services.
    \item Built the web frontend using Angular and the backend using Spring Boot.
    \item Designed and deployed the mobile app in Flutter, enhancing service accessibility for end users.
    \end{itemize}}

    \customcventry{07/2022 ‐ 08/2022}{\href{https://estatmar.ma/}{Finso}}{Game Developer}{}{}{
    \begin{itemize}[leftmargin=0.8cm, itemsep=0pt, topsep=0pt]
    \item Designed and developed an educational mobile game for children using Unity.
    \item Created interactive gameplay focused on learning through play.
    \item Strengthened UX and animation logic in a real-world release context.
    \end{itemize}}


    % EDUCATION
    \vspace{-12pt}
    \section{Education}

\customcventry
    {2020 -- 2025}
    {\href{https://emsi.ma}{\textbf{EMSI – École Marocaine des Sciences de l’Ingénieur}}}
    {Master's in Software Engineering and Networks – MIAGE\\(Applied Methods for Business Management)}
    {}{}{}}

    \customcventry
        {Jul. 2024 ‐ Sep. 2024}
        {\href{https://www.alxafrica.com}{\textbf{ALX Academy}}}
        {Associate's Degree in Artificial Intelligence and Prompt Engineering}
        {}{}{
        \begin{itemize}[leftmargin=0.5cm, itemsep=0pt, topsep=0pt]
            \item ALX AiCE – AI Career Essentials
        \end{itemize}
        }


\vspace{-16pt}
\section{Certifications}
\vspace{-2pt}
\textit{All certificates below were earned via Coursera.}
\begin{itemize}[leftmargin=0.5cm, itemsep=0pt, topsep=0pt]
    \item \textbf{\href{https://www.coursera.org/account/accomplishments/verify/G178XXP17WQA}{Machine Learning with Python}} (IBM)
    \item \textbf{\href{https://www.coursera.org/account/accomplishments/records/M5RKGX36BAVA}{IBM Data Engineering}} (IBM)
    \item \textbf{\href{https://google.com}{Building Scalable Java Microservices with Spring Boot and Spring Cloud}} (Google Cloud)
    \item \textbf{\href{https://www.coursera.org/account/accomplishments/verify/EK5SJM3YM7PX}{Introduction to Big Data with Spark and Hadoop}} (IBM)
    \item \textbf{\href{https://www.coursera.org/account/accomplishments/specialization/B4RCUAYCUG49}{Python for Everybody Specialization}} (University of Michigan)
    \item \textbf{\href{https://www.coursera.org/account/accomplishments/records/G867SJLRFQS2}{Google Business Intelligence}} (Google)
\end{itemize}

% EXTRACURRICULAR ACTIVITIES
\vspace{-12pt}
\section{Extracurricular Activities}
\vspace{-2pt}
\noindent\textbf{Sponsorship \& Gaming Lead, F\&G EMSI Club} \\
Managed Gaming event logistics and sponsor relationships for the F\&G EMSI club. Strengthened partnerships, increased visibility, and enhanced my communication and negotiation skills.


    % SKILLS
    \vspace{-14pt}
    \section{Skills}
    \vspace{-2pt}
    \begin{itemize}[leftmargin=0.5cm, itemsep=0pt, topsep=0pt]
    \item \textbf{Data Engineering:} ETL, Apache NiFi, Spark, Beam, PostgreSQL, GCP, AWS
    \item \textbf{Programming:} C, Python (pandas, FastAPI), SQL (PostgreSQL, MySQL), Java, TypeScript 
    \item \textbf{Web/Mobile Dev:} React, Next.js, Flutter, Spring boot, REST APIs
    \item \textbf{DevOps:} Agility, Docker, Kubernetes, Git, GitLab CI/CD, Linux
    \item \textbf{Visualization:} Metabase, Superset, Power BI
    \item \textbf{Soft Skills:} Teamwork, Communication, Adaptation, Problem Solving
    \end{itemize}

 
\vspace{-15pt}
\section{Languages}
\vspace{-15pt}
\begin{multicols}{2}
\begin{itemize}[leftmargin=0.3cm, itemsep=0pt, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item \textbf{English} – Fluent
    \item \textbf{French} – Fluent
    \item \textbf{Arabic} – Native
    \item \textbf{Spanish} – Basic
\end{itemize}
\end{multicols}
\vspace{-8pt}
\end{document}