    \documentclass[12pt,a4paper,sans]{moderncv}
    \moderncvstyle{banking}
    \moderncvcolor{black}
    \nopagenumbers{}

    \usepackage[utf8]{inputenc}
    \usepackage[top=1.5cm, bottom=1.5cm, left=1.5cm, right=1.5cm]{geometry} % standard margins
    \usepackage{ragged2e}
    \usepackage{multicol}
    \usepackage{enumitem}
    \usepackage{amssymb}
    \usepackage{fontawesome5}
    \usepackage{xcolor}
    \usepackage{hyperref}
    \hypersetup{colorlinks=true, urlcolor=blue}


    % Custom cventry
    \newcommand*{\customcventry}[7][.10em]{%
    \begin{tabular}{@{}l}
        {\bfseries #4} \\
        {\itshape #3}
    \end{tabular}
    \hfill
    \begin{tabular}{l@{}}
        {\bfseries #5} \\
        {\itshape #2}
    \end{tabular}
    \ifx&#7&%
    \else{\\
    \begin{minipage}{\maincolumnwidth}%
        \footnotesize#7%
    \end{minipage}}\fi%
    \par\addvspace{#1}
    }

    \begin{document}

    % Ultra-compact header block
    \begin{center}
        {\fontsize{18}{20}\selectfont\textbf{Ahmed MAKROUM}} \\
        \vspace{0.3em}
        \footnotesize Data Engineer and Full-Stack Web/Mobile Developer \\
        \vspace{0.3em}
        {\normalsize
            \faMobile\enspace +212 6 64 71 52 19 \quad
            \faEnvelope\enspace ahmedmakroum3@gmail.com \quad
            \faHome\enspace Casablanca, Morocco \\
            \faLinkedin\enspace \href{https://www.linkedin.com/in/ahmed-makroum/}{in/ahmedmakroum} \quad
            \faGithub\enspace \href{https://github.com/ahmedmakroum}{github.com/ahmedmakroum} \quad
            \faGlobe\enspace \href{https://ahmedmakroum.github.io/AhmedMakroumPortfolio/}{makroum.me}
        }
    \end{center}

    % PROFILE
\section{Profile}
\justifying
Results-driven Computer and Network Engineer (MIAGE: Applied Methods for Business Management) with a strong foundation in software engineering, data engineering, and full-stack development. Adept at building robust data pipelines, developing scalable web/mobile applications, and leveraging cloud and open-source technologies. Recognized for adaptability, teamwork, and a passion for continuous learning.
\vspace{1em}


%EXP%
    \section{Experience}

    \customcventry{03/2025 ‐ Present}{\href{https://www.allianz.ma}{Allianz Maroc}}{Data Engineer}{}{}{
    \begin{itemize}[leftmargin=0.5cm, itemsep=0pt, topsep=0pt]
    \item Designed and deployed end-to-end data pipelines using NiFi and Spark to extract, clean, and load data from internal insurance systems.
    \item Consolidated fragmented sources into a PostgreSQL warehouse, enabling unified and consistent reporting.
    \item Delivered real-time dashboards with Metabase, improving data accessibility for business users.
    \item Currently developing and maintaining a web application to manage and track healthcare payments issued by Allianz to external providers, using Spring Boot and Next.js.
    \end{itemize}}

    \customcventry{06/2024 ‐ 08/2024}{\href{https://boti.education/}{BOTI School}}{Data Engineer}{}{}{
    \begin{itemize}[leftmargin=0.8cm, itemsep=0pt, topsep=0pt]
    \item Developed a scalable ETL pipeline using Apache Beam on Google Cloud to process learning activity logs.
    \item Transformed raw data into structured datasets, enabling clear insights into user behavior and engagement.
    \item Delivered automated reporting through Looker dashboards for the executive team.
    \end{itemize}}

    \customcventry{06/2023 ‐ 08/2023}{\href{https://6solutions.com/}{6solutions}}{Web and Mobile Developer}{}{}{
    \begin{itemize}[leftmargin=0.8cm, itemsep=0pt, topsep=0pt]
    \item Developed a cross-platform consulting platform for legal, medical, and financial services.
    \item Built the web frontend using Angular and the backend using Spring Boot.
    \item Designed and deployed the mobile app in Flutter, enhancing service accessibility for end users.
    \end{itemize}}

    \customcventry{07/2022 ‐ 08/2022}{\href{https://estatmar.ma/}{Finso}}{Game Developer}{}{}{
    \begin{itemize}[leftmargin=0.8cm, itemsep=0pt, topsep=0pt]
    \item Designed and developed an educational mobile game for children using Unity.
    \item Created interactive gameplay focused on learning through play.
    \item Strengthened UX and animation logic in a real-world release context.
    \end{itemize}}

    % PROJECTS
    \section{Projects}
    \vspace{0.5em}
    \begin{itemize}[leftmargin=0.7cm, itemsep=2pt, topsep=2pt]
        \item \textbf{Moroccan Consulting Platform} (\href{https://6solutions.ma/}{6solutions}) – Led the development of a full-stack platform connecting users to legal, medical, and financial experts. Built with React, Flutter, Node.js, and PostgreSQL. \textit{Impact: Enabled 1000+ consultations in the first 3 months.}
        \item \textbf{Insurance Data Pipeline} (\href{https://www.allianz.ma/}{Allianz Maroc}) – Designed and deployed robust ETL pipelines using Apache NiFi and Spark to unify and expose insurance data for analytics and reporting.
        \item \textbf{Educational Game for Children} (\href{https://finso.ma/}{Finso}) – Developed a Unity-based mobile game to teach children basic math and logic through interactive play. \textit{Result: 500+ downloads in the first month.}
        \item \textbf{Cloud ETL for Learning Data} (\href{https://www.botischool.com/}{BOTI School}) – Built a scalable ETL pipeline on Google Cloud with Apache Beam, transforming and storing large-scale educational data for analytics.
        \item \textbf{Personal Portfolio Website} (\href{https://ahmedmakroum.github.io/AhmedMakroumPortfolio/}{makroum.me}) – Designed and deployed a modern, responsive portfolio to showcase projects and skills. Built with Next.js and hosted on GitHub Pages.
    \end{itemize}



    % EDUCATION
    \vspace{-3mm}
    \section{Education}

\customcventry
    {2020 -- 2025}
    {\href{https://emsi.ma}{\textbf{EMSI – École Marocaine des Sciences de l’Ingénieur}}}
    {Master's in Software Engineering and Networks – MIAGE\\(Applied Methods for Business Management)}
    {}{}{}}

    \customcventry
        {Jul. 2024 ‐ Sep. 2024}
        {\href{https://www.alxafrica.com}{\textbf{ALX Academy}}}
        {Associate's Degree in Artificial Intelligence and Prompt Engineering}
        {}{}{
        \begin{itemize}[leftmargin=0.5cm, itemsep=0pt, topsep=0pt]
            \item ALX AiCE – AI Career Essentials
        \end{itemize}
        }




    % CERTIFICATIONS
    \section{Certifications}
    \textit{All certificates below were earned via Coursera.}
    \begin{itemize}[leftmargin=0.7cm, itemsep=2pt, topsep=2pt]
        \item \textbf{\href{https://www.coursera.org/account/accomplishments/verify/G178XXP17WQA}{Machine Learning with Python}} (IBM)
        \item \textbf{\href{https://www.coursera.org/account/accomplishments/records/M5RKGX36BAVA}{IBM Data Engineering}} (IBM)
        \item \textbf{\href{https://www.coursera.org/account/accomplishments/verify/2QK7QK7QK7QK}{Google Business Intelligence}} (Google)
        \item \textbf{\href{https://google.com}{Building Scalable Java Microservices with Spring Boot and Spring Cloud}} (Google Cloud)
        \item \textbf{\href{https://www.coursera.org/account/accomplishments/verify/EK5SJM3YM7PX}{Introduction to Big Data with Spark and Hadoop}} (IBM)
        \item \textbf{\href{https://www.coursera.org/account/accomplishments/specialization/B4RCUAYCUG49}{Python for Everybody Specialization}} (University of Michigan)
    \end{itemize}



    \section{Skills}
    \begin{itemize}[leftmargin=0.5cm, itemsep=0pt, topsep=0pt]
    \item \textbf{Data Engineering:} ETL, Apache NiFi, Spark, Beam, PostgreSQL, GCP
    \item \textbf{Programming:} C, Python (pandas, FastAPI), SQL (PostgreSQL, MySQL), Java, TypeScript, 
    \item \textbf{Web/Mobile Dev:} React, Next.js, Flutter, Spring boot, REST APIs
    \item \textbf{DevOps:} Agility, Docker, Kubernetes, Git, GitLab CI/CD, Linux
    \item \textbf{Visualization:} Metabase, Superset, Power BI
    \item \textbf{Soft Skills:} Teamwork, Communication, Adaptation, Problem Solving
    \end{itemize}

    % EXTRACURRICULAR ACTIVITIES
    \section{Extracurricular Activities}
Managed Gaming event logistics and sponsor relationships for the F\&G EMSI club. Strengthened partnerships, increased visibility, and enhanced my communication and negotiation skills.

    % LANGUAGES
    \section{Languages}
    \begin{multicols}{2}
    \begin{itemize}[leftmargin=0.7cm, itemsep=2pt, topsep=2pt]
        \item \textbf{English} – Fluent
        \item \textbf{French} – Fluent
        \item \textbf{Arabic} – Native
        \item \textbf{Spanish} – Basic
    \end{itemize}
    \end{multicols}



    % FOOTER
\vspace{1em}
\begin{center}
    {\footnotesize\color{gray}
    To learn more about my projects and skills, feel free to check out my~
    \faLinkedin~\href{https://www.linkedin.com/in/ahmed-makroum/}{LinkedIn}~or~\faGithub~\href{https://github.com/ahmedmakroum}{GitHub}.}
\end{center}



    \end{document}
